Carbonate chemistry at Ny-Ålesund

### 2021-08-25 awipev-CO2.Rmd

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2

>>>>

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2
=======
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
```

The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
>>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb
